### 2017-02-28 paper/chapters/abstract.tex
change abstract to be an actual abstract
improve abstract (more text, what we discuss, etc.)

\section{Abstract}
\label{sec:abstract}
%One of the key aspects of human intelligence is the ability to construct accurate and generalized internal representations by observing high-dimensional data.
%We present several deep directed generative models aiming to learn rich and hierarchical latent structures, either implicitly or explicitly, as well as transforming them back into input space.

Deep directed generative models leverage the possibilities of deep learning to learn rich, hierarchical structures from datasets in a possibly unsupervised context.
These models can be used to understand high-dimensional, real-world data and transform them into compact representations. Similar to how humans learn to generalize from sensory input, we discuss several models which can learn compact, internal representational structures.
In this article, we will focus on two recently proposed architectures, variational autoencoders, and generative adversarial networks.

@@

>>>>

\begin{abstract}
%One of the key aspects of human intelligence is the ability to construct accurate and generalized internal representations by observing high-dimensional data.
%We present several deep directed generative models aiming to learn rich and hierarchical latent structures, either implicitly or explicitly, as well as transforming them back into input space.

Deep directed generative models leverage the possibilities of deep learning to learn rich, hierarchical structures from datasets in a possibly unsupervised context.
These models can be used to understand high-dimensional, real-world data and transform them into compact representations. Similar to how humans learn to generalize from sensory input, we discuss several models which can learn compact, internal representational structures.
After discussing generative modeling in general and its applications, we then introduce the sigmoid belief network which is a simple generative architecture.
Then we focus on two more recently proposed architectures: the variational autoencoders (VAE), and generative adversarial networks (GAN).
We discuss the key idea of both models and their respective learning and training procedure, including variational inference and adversarial training for VAE and GAN respectively.
Additionally to the originally proposed models, we summarize several extensions and present experimental results for the variational autoencoder.

%In this article, we will focus on two recently proposed architectures, variational autoencoders, and generative adversarial networks.

@@

\end{abstract}
